Non-kissing versus non-crossing

### 2018-11-08 secondPaper/FPSAC/nonkissing-noncrossing-FPSAC.tex
PEPS Pierre-Guy
corrections mineures

%% define your authors in the usual way
%% use \addressmark{1}, \addressmark{2} etc for the institutions, and use \thanks{} for contact details
\author{
	Yann Palu\thanks{\href{mailto:yann.palu@u-picardie.fr}{yann.palu@u-picardie.fr}. Supp. by ANR SC3A~15\,CE40\,0004\,01.}\addressmark{1},
	\stepcounter{footnote}
	Vincent Pilaud\thanks{\href{mailto:vincent.pilaud@lix.polytechnique.fr}{vincent.pilaud@lix.polytechnique.fr}. Supp. by ANR SC3A~15\,CE40\,0004\,01 and CAPPS~17\,CE40\,0018.}\addressmark{2},
	\and
	Pierre-Guy Plamondon\thanks{\href{mailto:pierre-guy.plamondon@math.u-psud.fr}{pierre-guy.plamondon@math.u-psud.fr}. Supp. by ANR SC3A~15\,CE40\,0004\,01.}\addressmark{3}
}

@@

This extended abstract reports on~\cite{PaluPilaudPlamondon-surfaces}, where more details and proofs are available.~It aims to show that two combinatorial objects, called the \emph{non-kissing complex} and the \emph{non-crossing complex}, are isomorphic.
Both complexes appeared in different works in specific cases: the non-kissing complex of a grid appeared in \cite{McConville}, while the non-crossing complex of a disk appeared in \cite{GarverMcConville, MannevillePilaud-accordion}.
It was shown in \cite{PaluPilaudPlamondon} that these complexes are special cases of a more general simplicial complex, defined for any gentle algebra (see~also~\cite{BrustleDouvilleMousavandThomasYildirim}).

>>>>

%% define your authors in the usual way
%% use \addressmark{1}, \addressmark{2} etc for the institutions, and use \thanks{} for contact details
\author{
	Yann Palu\thanks{\href{mailto:yann.palu@u-picardie.fr}{yann.palu@u-picardie.fr}. Supp. by ANR SC3A~15\,CE40\,0004\,01.}\addressmark{1},
	\stepcounter{footnote}
	Vincent Pilaud\thanks{\href{mailto:vincent.pilaud@lix.polytechnique.fr}{vincent.pilaud@lix.polytechnique.fr}. Supp. by ANR SC3A~15\,CE40\,0004\,01 and CAPPS~17\,CE40\,0018.}\addressmark{2},
	\and
	Pierre-Guy Plamondon\thanks{\href{mailto:pierre-guy.plamondon@math.u-psud.fr}{pierre-guy.plamondon@math.u-psud.fr}. Supp. by ANR SC3A~15\,CE40\,0004\,01 and a PEPS JCJC.}\addressmark{3}
}

@@

This extended abstract reports on~\cite{PaluPilaudPlamondon-surfaces}, where more details and proofs are available.~It shows that two combinatorial objects, the \emph{non-kissing complex} and the \mbox{\emph{non-crossing complex}}, are isomorphic.
Both complexes appeared in different works in specific cases: the non-kissing complex of a grid appeared in \cite{McConville}, while the non-crossing complex of a disk appeared in \cite{GarverMcConville, MannevillePilaud-accordion}.
It was shown in \cite{PaluPilaudPlamondon} that these complexes are special cases of a more general simplicial complex, defined for any gentle algebra (see~also~\cite{BrustleDouvilleMousavandThomasYildirim}).
